Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-13 chapters/paper2.tex
Streamlined introduction

This study investigates the post-formation structural response of bijels stabilized by ellipsoidal magnetic particles under the influence of externally applied magnetic fields. 
Using a hybrid Lattice Boltzmann Method coupled with Molecular Dynamics, we simulate the formation and evolution of bijel structures stabilized by rod-like particles modeled as 
magnetic dipoles. We find that increasing the applied magnetic field after formation induces microstructural changes characterized by increased domain anisotropy and 
coarsening, up to a saturation threshold. In contrast, decreasing or removing the magnetic field results in minimal morphological change, suggesting that the structure is
resilient to removal of stimuli. Analysis reveals that particle unjamming, reorientation at the interface, and subsequent re-jamming are responsible for these structural transformations.

To understand the saturation behavior, we applied magnetic fields of varying strength to bijel templates formed under increasing initial field conditions. We observed that 
a greater initial nematic order parameter negatively correlated with the extent of microstructure change. Finally, switching off the magnetic field in pre-aligned bijels had little 
impact on the microstructure, indicating that the jammed interfacial network prevents reversal of anisotropic features. These findings underscore the importance of processing 
history and demonstrate how magnetic field manipulation, in combination with anisotropic particle stabilization, enables tunable, on-demand microstructure control in bijels, 
offering new capabilities for adaptive material design.

>>>>

This study investigates the post-formation structural response of bijels stabilized by ellipsoidal magnetic particles under the influence of externally applied magnetic fields. 
Using a hybrid Lattice Boltzmann Method coupled with Molecular Dynamics, we simulate the formation and evolution of bijel structures stabilized by rod-like particles modeled as 
magnetic dipoles. We find that increasing the applied magnetic field after formation induces microstructural changes characterized by increased domain anisotropy and 
coarsening, up to a saturation threshold. In contrast, decreasing or removing the magnetic field results in minimal morphological change, suggesting that the structure is
resilient to removal of stimuli. Analysis reveals that particle unjamming, reorientation at the interface, and subsequent re-jamming are responsible for these structural transformations.
These findings demonstrate how magnetic field manipulation, in combination with ellipsoidal particle stabilization, enables tunable, on-demand microstructure 
control in bijels, offering new capabilities for adaptive material design.

% To understand the saturation behavior, we applied magnetic fields of varying strength to bijel templates formed under increasing initial field conditions. We observed that 
% a greater initial nematic order parameter negatively correlated with the extent of microstructure change. Finally, switching off the magnetic field in pre-aligned bijels had little 
% impact on the microstructure, indicating that the jammed interfacial network prevents reversal of anisotropic features.
